### 2024-07-31 conteudo/eval/eval.tex
do triangulation

\subsection{Discussion}

>>>>

\subsection{Triangulation of results}

Both the BigCloneBench and the empirical method results point out that our tool has a good 
result for detecting Type-1 and Type-2 code clone duplications and has a poor performance 
in detecting the other types. Using a similarity metric between 80\% and 100\% shows good 
results in both methods.

There is a discrepancy in the results of non-code duplications inferred as duplications 
between the two methods. In the BigCloneBench results, we did not find any negative samples,
while in the empirical analyses, we found a higher percentage of negative samples. We have 
two possible reasons for this discrepancy.

The first reason is the limitations and problems of the BigCloneBench presented by Krinke 
and Ragkhitwetsagul \citep{bigfail}. The second reason is that the AMD Display driver 
is a system where each code artifact shares a meaning. While the BigCloneBench is a 
collection of self-contained code artifacts without sharing meaning with each, as our 
tool uses a text-based code clone detection method, it is expected to have poorer 
performance in the AMD Display driver than in the BigCloneBench dataset. We do not know 
if the state-of-the-art code duplication detection has the same problem and is obscured 
by the evaluation in the BigCloneBench dataset.
